\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in R

### 2014-01-11 papers/jss/article.Rnw
another one
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@743 edb9625f-4e0d-4859-8d74-9fd3b1da38cb
fix
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@746 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\begin{itemize}
\item \emph{Portable}:  Allows users to send and receive data between
  applications or different computers.
\item \emph{Efficient}:  Data is serialized into a compact binary
  representation for transmission or storage.
\item \emph{Exentsible}:  New fields can be added to Protocol Buffer Schemas
  in a forward-compatible way that do not break older applications.
\item \emph{Stable}:  Protocol Buffers have been in wide use for over a
  decade.
\end{itemize}

@@

The example above shows how the \texttt{HTTP GET} method retrieves a 
resource from OpenCPU, for example an R object. The \texttt{HTTP POST} 
method on the other hand is used for calling functions and running scripts, 
which is the primary purpose of the framework. As before, the \texttt{/pb} 
postfix requests to retrieve the output as a protobuf message, in this
case the function return value. However, OpenCPU allows us to supply the
arguments of the function call in the form of protobuf messages as well.
This is a bit more work, because clients needs to both generate messages 
containing R objects to post to the server, as well as retrieve and parse
protobuf messages returned by the server. Using protocol buffers to post
function arguments is not required, and for simple (scalar) arguments 
the standard \texttt{application/www-url-encoded} format might be sufficient.
However, with protocol buffers the client can perform function calls with
more complex arguments such as R vectors or lists. The result is a complete
RPC system to do arbitrary R function calls from within 
any programming language.

>>>>

\begin{itemize}
\item \emph{Portable}:  Allows users to send and receive data between
  applications or different computers.
\item \emph{Efficient}:  Data is serialized into a compact binary
  representation for transmission or storage.
\item \emph{Extensible}:  New fields can be added to Protocol Buffer Schemas
  in a forward-compatible way that do not break older applications.
\item \emph{Stable}:  Protocol Buffers have been in wide use for over a
  decade.
\end{itemize}

@@

The example above shows how the \texttt{HTTP GET} method retrieves a 
resource from OpenCPU, for example an R object. The \texttt{HTTP POST} 
method on the other hand is used for calling functions and running scripts, 
which is the primary purpose of the framework. As before, the \texttt{/pb} 
postfix requests to retrieve the output as a protobuf message, in this
case the function return value. However, OpenCPU allows us to supply the
arguments of the function call in the form of protobuf messages as well.
This is a bit more work, because clients needs to both generate messages 
containing R objects to post to the server, as well as retrieve and parse
protobuf messages returned by the server. Using protocol buffers to post
function arguments is not required, and for simple (scalar) arguments 
the standard \texttt{application/x-www-form-urlencoded} format might be sufficient.
However, with protocol buffers the client can perform function calls with
more complex arguments such as R vectors or lists. The result is a complete
RPC system to do arbitrary R function calls from within 
any programming language.
